\section{Experimental Design}

In our experimental study, we set $\mathit{differanceTolerance}$ to
$0.40$. This value was chosen by performing doubling
experiments on various algorithms with known worst case time
complexities, and observing that the ratio converged to the correct
value when $\mathit{diff} < 0.40$.

We set $\mathit{doublesTolerance}$ to $20$ after observing that
\textit{SchemaAnalyst} stopped displaying constant behavior after around
5 doubles.

To analyze \textit{SchemaAnalyst}, the iTrust and NistWeather case
studies provided by \textit{SchemaAnalyst} were used as the initial 
input schemas.
Both of these schemas are taken from real world applications. The factor $n$
under study was the number of check constraints present on the schema.  
A Java program was
implemented to double the number of these constraints. Generating
synthetic check constraints is non-trivial because there are many
possible check constraints, and generating a constraint that is
unsatisfiable might cause the data generation tool to take a longer
amount of time than should be the case. To avoid this problem, we
instead duplicate the existing check constraints present on the schema
rather than attempt to generate new ones. This technique is easy
to implement and ensures that the check constraints added are
semantically valid.  For every table in the input schema, the tool 
duplicated the existing check constraints and added the duplicates 
to the table.  

The test suite generation tool provided by \textit{SchemaAnalyst}
requires a coverage criterion and a data generator to be specified. A
coverage criterion is a system of rules that generate test requirements
\cite{Ammann:Testing}. The data generator is the object that generates
the test data according to the rules specified by the coverage
criterion. The criterion used in the experiment was
\textsc{constraintCACCoverage}, 
the data generator was \textsc{directedRandom}. The
doubling experimentation software were implemented in Java, and were both compiled and run using
version 1.7 of the compiler and Java Virtual Machine. The experiment was executed on an Ubuntu 13.10 machine with a 2.4
GHz quad core CPU running the 3.11.0-18-generic x86\_64 GNU/Linux
kernel and 4GB of memory.
