%!TEX root=../seke.tex
% mainfile: ../seke.tex

\vspace*{-.25in}
\section{Introduction}
\vspace*{-.05in}

% GMK NOTE: Removing the reference to the Walcott paper, not absolutely critical.

% Search-based algorithms allow the application of guidance to problems.
% The algorithm attempts to improve a potential
% solution until it is acceptable according to a fitness function.

Many disciplines, such as science, finance, and medicine, rely on relational databases to maintain large amounts of
critical information~\cite{kapfhammer2007}. The relational database schema defines the structure of a database and
protects the integrity of the data. This makes testing the database schema necessary to avoid the corruption of data.
Search-based algorithms, that use a fitness function to offer guidance to the correct solution, have been applied to
this challenging problem~\cite{Kapfhammer2013}. Although data generation for relational schemas may also be solved,
albeit less effectively, with random generation schemes~\cite{McMinn2015}, the use of search-based methods ensures that
data creation methods can actively seek out test inputs that best fulfill testing goals~\cite{McMinn2004a}.

% GMK NOTE: Revised this content in the paragraph above and below

% Without the use of a search-based strategy, a problem might be approached with a random sampling or greedy technique.
% In the domain of data generation for software testing, this means that rather than randomly selecting inputs from a
% program’s input space, the data generator can actively seek out qualities of an input that best fulfills the test’s
% goals~\cite{McMinn2004a}.

Despite the effectiveness of search-based data generation methods, there is, to the best of our knowledge, no research
that fully studies their efficiency and characterizes their worst-case time complexity. In part, we attribute this
dearth of prior work to the fact that these systems are complex and thus often difficult to analyze theoretically.

In response to this lack of insight into the performance of search-based methods, this paper presents a fully automated
performance evaluation framework that employs doubling experiments to suggest worst-case time complexities and
classification and regression trees to identify efficiency trends. Applying this framework to the automated performance
evaluation of search-based test data generation for database schemas, the results reveal trade-offs in efficiency with
respect to the chosen testing goals, the structure of the relational schema, and the data generation strategy.

Since the presented approach is fully automated, it enabled a comprehensive study suggesting the worst-case time
complexity of all the relevant data generator configurations. Although this paper focuses on automatically evaluating
efficiency of search-based test data generation for database schemas, the presented technique is general and thus
applicable to a wide range of methods using heuristic search. In summary, this paper's important \mbox{contributions
include}:

% GMK NOTE: I captured the essence of this content and then made room for another key point

% attack the performance evaluation of search-based test data generation with an empirical
% approach. We present an empirical performance study of the search-based test data generation tool, called
% \textit{SchemaAnalyst}, which generates test suites for relational database schemas. To evaluate worst-case performance,
% we developed a technique for automatically conducting doubling experiments. Using this process, we explored
% \textsc{xmany} configurations of \textit{SchemaAnalyst}, revealing
% Our automatic technique enabled a comprehensive empirical study, that would otherwise have been infeasible, and the
% results have important practical significance for the selection of parameters in search-based test data generation
% tools.

\begin{enumerate}
  \itemsep0in

  \item A performance evaluation framework that automatically conducts and analyzes the results from doubling
    experiments with search-based methods.

  \item With a systematic focus on a wide variety of configurations, an empirical study revealing trade-offs
    in search-based test data generation for relational schemas.

  \item Empirically derived suggestions for the worst-case time complexity of search-based test data generators.

  \end{enumerate}
  \vspace*{-.2in}
