%!TEX root=seke.tex
% mainfile: ../seke.tex

While the box and whisker plots allow us to see how choices between coverage criterions and data generators affects
runtime, the question remains if these differences are statistically and practically significant. To answer this
question, we calculate the Wilcoxon rank sum test and the $\hat{A}_{12}$ test.

We perform these tests for every pair of coverage criterions, and every pair of data generators.  Table~\ref{tab:crites}
shows the results of these tests for coverage criteria, and Table~\ref{tab:datas} shows the results for data generators.

The Wilcoxon rank sum test is a nonparematric test for hypothesis
testing.  If the result of the test is greater than the significance
level ($0.05$ is frequently used), then the collections are
indistingushable.  If however, the result is less, then the collections
are differentiable.  The $\hat{A}_{12}$ test is similar, but for drawing
conclusions about the pratical differance between two collections of
data.  A result $a=0.5$0 means that any differance is not pratically
significant, while $a>0.56$ or $a<0.44$ signifies a small differnace,
$a>0.64$ or $a<0.36$ denotes a medium differance, and $a>0.71$ or
$a<0.29$ indicates a large differance. 

Table~\ref{tab:crites} reveals that changing the criterion results in
satistically significant differances in runtimes, with the excpetion of
changing between four constraints at the top of the subsumption
heirarchy, and two constraints at the bottom.  The $\hat{A}_{12}$
results generally show a small to medium practical effect of switching
between criterions at the high or low end of the herirchy, and small or
no effect of switching between constraints at the same level of the
heriarchy.

% This table might be on the chopping block
Table~\ref{tab:datas} shows a statistically significant differance
between all pairs of data generators. The $\hat{A}_{12}$ results all
choices in data generator have at least a small pratical impact, with
the exeption of choosing between random and random defaults, and
directed random and directed random defaults.  Change between these sets
of data generators results in a large to medium effect, and compairing
either AVM data generator to another primarily resulted in a small
differance.

\begin{table*}[h]
\begin{tabular}{llllllllll}
           & APC      & ANCC     & CondAICC & NCC      & AUCC     & AICC     & ClauseAICC & ICC      & UCC   \\
APC        & NA       & \cellcolor{gray!25}0.425    &
\cellcolor{gray!45}0.337    & 0.484    &\cellcolor{gray!45} 0.334    &
\cellcolor{gray!25}0.413    &\cellcolor{gray!45} 0.329      & 0.481    & 0.449 \\
ANCC       & 2.20E-16 & NA       &\cellcolor{gray!25} 0.407
&\cellcolor{gray!25} 0.561    &\cellcolor{gray!25} 0.405    & 0.484
&\cellcolor{gray!25} 0.399      & 0.554    & 0.526 \\
CondAICC   & 2.20E-16 & 2.20E-16 & NA       &\cellcolor{gray!45} 0.671
& 0.503    &\cellcolor{gray!25} 0.581    & 0.492
&\cellcolor{gray!45} 0.656    &\cellcolor{gray!25} 0.634 \\
NCC        & 1.20E-02 & 2.20E-16 & 2.20E-16 & NA
&\cellcolor{gray!45} 0.335    &\cellcolor{gray!25} 0.417
&\cellcolor{gray!45} 0.322      & 0.491    & 0.461 \\
AUCC       & 2.20E-16 & 2.20E-16 & \cellcolor{gray!65}6.92E-01 & 2.20E-16 & NA       &
\cellcolor{gray!25}0.577    & 0.490      &\cellcolor{gray!45} 0.651
&\cellcolor{gray!25} 0.628 \\
AICC       & 2.20E-16 & 1.70E-02 & 2.20E-16 & 2.20E-16 & 2.20E-16 & NA
&\cellcolor{gray!25} 0.412      &\cellcolor{gray!25} 0.571    & 0.547 \\
ClauseAICC & 2.20E-16 & 2.20E-16 & \cellcolor{gray!65}2.72E-01 & 2.20E-16 & 1.40E-01 &
2.20E-16 & NA         & \cellcolor{gray!45}0.662    &\cellcolor{gray!45} 0.641 \\
ICC        & 4.00E-03 & 2.20E-16 & 2.20E-16 &\cellcolor{gray!65} 1.83E-01 & 2.20E-16 & 2.20E-16 & 2.20E-16   & NA       & 0.472 \\
UCC        & 9.30E-16 & 3.83E-05 & 2.20E-16 & 7.36E-10 & 2.20E-16 & 5.73E-13 & 2.20E-16   & 9.29E-06 & NA    \\
\end{tabular}
\caption{For each pair of coverage criterions, lower left shows Wilcox
Rank Sum Test, upper right shows $\hat{A}_{12}$.}
\label{tab:crites}
\end{table*}


\begin{table*}[h]
\begin{tabular}{lllllll}
                         & Random   & Random Defaults & Directed Random & Directed Random Defaults & AVM      & AVM Defaults \\
Random                   & NA       & 0.538
&\cellcolor{gray!65} 0.740           &\cellcolor{gray!65} 0.789
&\cellcolor{gray!25} 0.627    &\cellcolor{gray!45} 0.680        \\
Random Defaults          & 6.59E-13 & NA              &
\cellcolor{gray!45}0.673           &\cellcolor{gray!45} 0.701
&\cellcolor{gray!25} 0.564    & \cellcolor{gray!25}0.617        \\
Directed Random          & 2.20E-16 & 2.20E-16        & NA
& 0.543                    &\cellcolor{gray!25} 0.360    &\cellcolor{gray!25} 0.435        \\
Directed Random Defaults & 2.20E-16 & 2.20E-16        & 9.74E-16
& NA                       &\cellcolor{gray!45} 0.328    &\cellcolor{gray!25} 0.395        \\
AVM                      & 2.20E-16 & 2.20E-16        & 2.20E-16
& 2.20E-16                 & NA       &\cellcolor{gray!25} 0.572        \\
AVM Defaults             & 2.20E-16 & 2.20E-16        & 2.20E-16        & 2.20E-16                 & 2.20E-16 & NA
\end{tabular}
\caption{For each pair of Data Generators, lower left shows Wilcox Rank
Sum Test, upper right shows $\hat{A}_{12}$.}
\label{tab:datas}
\end{table*}
